DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-02-26 scnn.tex
thanks reviewers in paper

This work was supported by a grant from the Swiss Data Science Centre (SDCS) under project \textit{DLOC:  Deep Learning for Observational Cosmology} and grant number 200021\_169130 from the Swiss National Science Foundation.
We thank Jean-François Cardoso for helpful discussions about the spherical harmonics.
We thank Alexandre Refregier, Adam Amara, Thomas Hofmann and Fernando Perez-Cruz for advice and helpful discussions.
We thank Hamsa Padmanabhan for testing use cases of the code.

>>>>

This work was supported by a grant from the Swiss Data Science Center (SDCS) under project \textit{DLOC:  Deep Learning for Observational Cosmology} and grant number 200021\_169130 from the Swiss National Science Foundation (SNSF).
We thank Jean-François Cardoso for helpful discussions about the spherical harmonics.
We thank Alexandre Refregier, Adam Amara, Thomas Hofmann, and Fernando Perez-Cruz for advice and helpful discussions.
We thank Hamsa Padmanabhan for testing use cases of the code.
Finally, we thank the two anonymous reviewers who provided extensive feedback that greatly improved the quality of this paper.
